---
title: "itsjon_OriginalHomeworkCode_02"
author: "Jonathan Zhang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set Up

```{r}
mean_calls <- 15
```

## Questions

# What is the probability that she will hear more than 8 calls during any given session?

```{r}
p_more_than_8 <- 1 - ppois(8, mean_calls)
cat("P(X > 8):", round(p_more_than_8, 4), "\n")
```

# What is the probability that she will hear no calls in a session?

```{r}
p_zero_calls <- dpois(0, mean_calls)
cat("P(X = 0):", round(p_zero_calls, 4), "\n")
```

# What is the probability that she will hear exactly 3 calls in a session?

```{r}
p_three_calls <- dpois(3, mean_calls)
cat("P(X = 3):", round(p_three_calls, 4), "\n")
```

# Plot the relevant Poisson mass function over the values in range 0 ≤ x ≤ 30.

```{r}
x_values <- 0:30
plot_mass_values <- dpois(x_values, mean_calls)
plot(x_values, plot_mass_values, type = "h", lwd = 2, col = "blue",
main = "Poisson Probability Mass Function (mean_calls = 15)",
xlab = "Number of Calls", ylab = "Probability")
points(x_values, plot_mass_values, pch = 16, col = "black")
```

# Simulate 104 results from this distribution (i.e., 2 years of Saturday monitoring sessions).

```{r}
set.seed(42)
two_years_data <- rpois(104, mean_calls)
```

# Plot the simulated results using hist() and use xlim() to set the horizontal limits to be from 0 to 30. How does your histogram compare to the shape of the probability mass function you plotted above?

```{r}
hist(two_years_data, breaks = 30, freq = FALSE, col = "red",
main = "Simulated Poisson Distribution (104 sessions)",
xlab = "Number of Calls", xlim = c(0, 30))
lines(x_values, plot_mass_values, type = "b", col = "black", lwd = 2, pch = 16)
```
#Comments: Your calculations and Poisson probabilities and simulations look correct and well structured. You've also effectively used ppois() and dpois() for your calculations and rpois() for simulation. The code is also well organized and easy to follow with your comments on each step of the process. The probability mass function (PMF) plot is well-constructed with plot() and points(), and the histogram includes lines() to overlay the theoretical PMF on the simulated data, which is a great way to compare them. 